The User Behavior On Online Judge Website

### 2017-05-13 paper.tex
Windows cracks again, let me backup it as soon as possible.

\[
solve_i = \beta_1 solve_{i-1} + \beta_2 hard \, solve_{i-1} + \epsilon_i
\]

@@

@@

We would like to see the later problem tend to face to buru solver, so the difficulty effect will decrease.

@@

Conclusion content.

>>>>

\[
solve_i = \beta_1 solve_{i-1} + \beta_2 hard_i \, solve_{i-1} + \epsilon_i
\]

@@

If a solver encounter a hard problem that he can't solve, he may drop the website or wait to time that he can
solve it, that is what above model want to match. But we can consider another behavior in which solver will
try to skip the problem and to solve the next one. If the hard problem is \textit{isolated}, we can expect
the decrease shock caused by the problem will be compressd. For match this, I specify the 2 lag item:

\[
solve_i = \beta_1 solve_{i-1} + \beta_2 solve_{i-2} + \beta_3 hard_i \, solve_{i-1} + \epsilon_i
\]

\begin{center}
\begin{tabular}{lclc}
\toprule
\textbf{Dep. Variable:}     &      solve       & \textbf{  R-squared:         } &     0.961   \\
\textbf{Model:}             &       OLS        & \textbf{  Adj. R-squared:    } &     0.960   \\
\textbf{Method:}            &  Least Squares   & \textbf{  F-statistic:       } &     2099.   \\
\textbf{Date:}              & Sat, 13 May 2017 & \textbf{  Prob (F-statistic):} & 2.30e-180   \\
\textbf{Time:}              &     09:37:24     & \textbf{  Log-Likelihood:    } &   -2797.0   \\
\textbf{No. Observations:}  &         260      & \textbf{  AIC:               } &     5600.   \\
\textbf{Df Residuals:}      &         257      & \textbf{  BIC:               } &     5611.   \\
\textbf{Df Model:}          &           3      & \textbf{                     } &             \\
\bottomrule
\end{tabular}
\begin{tabular}{lccccc}
                            & \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$>$$|$t$|$} & \textbf{[95.0\% Conf. Int.]}  \\
\midrule
\textbf{solve\_l1}           &       0.6957  &        0.060     &    11.564  &         0.000        &         0.577     0.814       \\
\textbf{solve\_l2}           &       0.1718  &        0.053     &     3.230  &         0.001        &         0.067     0.277       \\
\textbf{diff\_hard:solve\_l1} &      -0.3490  &        0.166     &    -2.101  &         0.037        &        -0.676    -0.022       \\
\bottomrule
\end{tabular}
\begin{tabular}{lclc}
\textbf{Omnibus:}       & 76.644 & \textbf{  Durbin-Watson:     } &    2.015  \\
\textbf{Prob(Omnibus):} &  0.000 & \textbf{  Jarque-Bera (JB):  } & 2966.655  \\
\textbf{Skew:}          & -0.202 & \textbf{  Prob(JB):          } &     0.00  \\
\textbf{Kurtosis:}      & 19.543 & \textbf{  Cond. No.          } &     22.4  \\
\bottomrule
\end{tabular}
%\caption{OLS Regression Results}
\end{center}

\[
solve_i = \beta_1 solve_{i-1} + \beta_2 solve_{i-2} + \beta_3 hard_i \, solve_{i-1} + \beta_4 hard \, solve_{i-2} + \epsilon_i
\]

\begin{center}
\begin{tabular}{lclc}
\toprule
\textbf{Dep. Variable:}     &      solve       & \textbf{  R-squared:         } &     0.961   \\
\textbf{Model:}             &       OLS        & \textbf{  Adj. R-squared:    } &     0.960   \\
\textbf{Method:}            &  Least Squares   & \textbf{  F-statistic:       } &     1569.   \\
\textbf{Date:}              & Sat, 13 May 2017 & \textbf{  Prob (F-statistic):} & 1.03e-178   \\
\textbf{Time:}              &     09:38:11     & \textbf{  Log-Likelihood:    } &   -2796.8   \\
\textbf{No. Observations:}  &         260      & \textbf{  AIC:               } &     5602.   \\
\textbf{Df Residuals:}      &         256      & \textbf{  BIC:               } &     5616.   \\
\textbf{Df Model:}          &           4      & \textbf{                     } &             \\
\bottomrule
\end{tabular}
\begin{tabular}{lccccc}
                            & \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$>$$|$t$|$} & \textbf{[95.0\% Conf. Int.]}  \\
\midrule
\textbf{solve\_l1}           &       0.7014  &        0.061     &    11.406  &         0.000        &         0.580     0.822       \\
\textbf{solve\_l2}           &       0.1667  &        0.054     &     3.064  &         0.002        &         0.060     0.274       \\
\textbf{diff\_hard:solve\_l1} &      -0.4368  &        0.253     &    -1.727  &         0.085        &        -0.935     0.061       \\
\textbf{diff\_hard:solve\_l2} &       0.1235  &        0.268     &     0.461  &         0.645        &        -0.405     0.652       \\
\bottomrule
\end{tabular}
\begin{tabular}{lclc}
\textbf{Omnibus:}       & 75.816 & \textbf{  Durbin-Watson:     } &    2.022  \\
\textbf{Prob(Omnibus):} &  0.000 & \textbf{  Jarque-Bera (JB):  } & 2893.093  \\
\textbf{Skew:}          & -0.178 & \textbf{  Prob(JB):          } &     0.00  \\
\textbf{Kurtosis:}      & 19.338 & \textbf{  Cond. No.          } &     46.5  \\
\bottomrule
\end{tabular}
%\caption{OLS Regression Results}
\end{center}

\[
solve_i = \beta_1 solve_{i-1} + \beta_2 solve_{i-2} + \beta_3 solve_{i-3} + \beta_4 hard_i \, solve_{i-1} + \epsilon_i
\]

\begin{center}
\begin{tabular}{lclc}
\toprule
\textbf{Dep. Variable:}     &      solve       & \textbf{  R-squared:         } &     0.968   \\
\textbf{Model:}             &       OLS        & \textbf{  Adj. R-squared:    } &     0.967   \\
\textbf{Method:}            &  Least Squares   & \textbf{  F-statistic:       } &     1910.   \\
\textbf{Date:}              & Sat, 13 May 2017 & \textbf{  Prob (F-statistic):} & 1.06e-188   \\
\textbf{Time:}              &     09:52:21     & \textbf{  Log-Likelihood:    } &   -2745.4   \\
\textbf{No. Observations:}  &         259      & \textbf{  AIC:               } &     5499.   \\
\textbf{Df Residuals:}      &         255      & \textbf{  BIC:               } &     5513.   \\
\textbf{Df Model:}          &           4      & \textbf{                     } &             \\
\bottomrule
\end{tabular}
\begin{tabular}{lccccc}
                            & \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$>$$|$t$|$} & \textbf{[95.0\% Conf. Int.]}  \\
\midrule
\textbf{solve\_l1}           &       0.5798  &        0.054     &    10.823  &         0.000        &         0.474     0.685       \\
\textbf{solve\_l2}           &       0.1711  &        0.062     &     2.741  &         0.007        &         0.048     0.294       \\
\textbf{solve\_l3}           &       0.1300  &        0.046     &     2.809  &         0.005        &         0.039     0.221       \\
\textbf{diff\_hard:solve\_l1} &      -0.3202  &        0.142     &    -2.247  &         0.025        &        -0.601    -0.040       \\
\bottomrule
\end{tabular}
\begin{tabular}{lclc}
\textbf{Omnibus:}       & 94.148 & \textbf{  Durbin-Watson:     } &     2.375  \\
\textbf{Prob(Omnibus):} &  0.000 & \textbf{  Jarque-Bera (JB):  } &  1219.969  \\
\textbf{Skew:}          &  1.042 & \textbf{  Prob(JB):          } & 1.22e-265  \\
\textbf{Kurtosis:}      & 13.426 & \textbf{  Cond. No.          } &      26.1  \\
\bottomrule
\end{tabular}
%\caption{OLS Regression Results}
\end{center}

\[
solve_i = \beta_1 solve_{i-1} + \beta_2 solve_{i-2} + \beta_3 solve_{i-3} + \beta_4 solve_{i-4} + \beta_5 hard_i \, solve_{i-1} + \epsilon_i
\]

\begin{center}
\begin{tabular}{lclc}
\toprule
\textbf{Dep. Variable:}     &      solve       & \textbf{  R-squared:         } &     0.973   \\
\textbf{Model:}             &       OLS        & \textbf{  Adj. R-squared:    } &     0.972   \\
\textbf{Method:}            &  Least Squares   & \textbf{  F-statistic:       } &     1820.   \\
\textbf{Date:}              & Sat, 13 May 2017 & \textbf{  Prob (F-statistic):} & 4.90e-196   \\
\textbf{Time:}              &     09:52:27     & \textbf{  Log-Likelihood:    } &   -2697.7   \\
\textbf{No. Observations:}  &         258      & \textbf{  AIC:               } &     5405.   \\
\textbf{Df Residuals:}      &         253      & \textbf{  BIC:               } &     5423.   \\
\textbf{Df Model:}          &           5      & \textbf{                     } &             \\
\bottomrule
\end{tabular}
\begin{tabular}{lccccc}
                            & \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$>$$|$t$|$} & \textbf{[95.0\% Conf. Int.]}  \\
\midrule
\textbf{solve\_l1}           &       0.3339  &        0.055     &     6.110  &         0.000        &         0.226     0.442       \\
\textbf{solve\_l2}           &       0.2081  &        0.055     &     3.776  &         0.000        &         0.100     0.317       \\
\textbf{solve\_l3}           &       0.0363  &        0.055     &     0.660  &         0.510        &        -0.072     0.145       \\
\textbf{solve\_l4}           &       0.2581  &        0.041     &     6.323  &         0.000        &         0.178     0.338       \\
\textbf{diff\_hard:solve\_l1} &      -0.2193  &        0.124     &    -1.767  &         0.079        &        -0.464     0.025       \\
\bottomrule
\end{tabular}
\begin{tabular}{lclc}
\textbf{Omnibus:}       & 135.383 & \textbf{  Durbin-Watson:     } &    2.179  \\
\textbf{Prob(Omnibus):} &   0.000 & \textbf{  Jarque-Bera (JB):  } & 1713.428  \\
\textbf{Skew:}          &   1.761 & \textbf{  Prob(JB):          } &     0.00  \\
\textbf{Kurtosis:}      &  15.123 & \textbf{  Cond. No.          } &     29.1  \\
\bottomrule
\end{tabular}
%\caption{OLS Regression Results}
\end{center}

To compare the four models, we can see the difficulty shock only exists one period (So solver can't
recall the hell except that is the last problem he try to solve.). And there's significance skip effect, I prefer
to choose the model 3 as real model, hence we can get the average transition diagram
from the estimated parameters to illustrate this:

\[
\begin{array}{c|ccccccc}
\mathrm{Hard} & 1 & 2& 3 & 4 & 5 & 6 &7 \\
\hline
\mathrm{EEEE} & 10000 & 9500 & 9000 & 8593 & 8164 & 7749 & 7386 \\
\mathrm{EEEH} & 10000 & 9500 & 9000 & 8593 & 8164 & 7749 & 4905 \\
\mathrm{EEHE} & 10000 & 9500 & 9000 & 8593 & 8164 & 5135 & 7046 \\
\mathrm{EEHH} & 10000 & 9500 & 9000 & 8593 & 8164 & 5135 & 5402 \\
\mathrm{EHEE} & 10000 & 9500 & 9000 & 8593 & 5413 & 7392 & 6869 \\
\mathrm{EHEH} & 10000 & 9500 & 9000 & 8593 & 5413 & 7392 & 4502 \\
\mathrm{EHHE} & 10000 & 9500 & 9000 & 8593 & 5413 & 5658 & 6644 \\
\mathrm{EHHH} & 10000 & 9500 & 9000 & 8593 & 5413 & 5658 & 4832 \\
\mathrm{HEEE} & 10000 & 9500 & 9000 & 5711 & 7790 & 7208 & 5581 \\
\mathrm{HEEH} & 10000 & 9500 & 9000 & 5711 & 7790 & 7208 & 3273 \\
\mathrm{HEHE} & 10000 & 9500 & 9000 & 5711 & 7790 & 4713 & 5257 \\
\mathrm{HEHH} & 10000 & 9500 & 9000 & 5711 & 7790 & 4713 & 3748 \\
\mathrm{HHEE} & 10000 & 9500 & 9000 & 5711 & 5961 & 6970 & 5237 \\
\mathrm{HHEH} & 10000 & 9500 & 9000 & 5711 & 5961 & 6970 & 3006 \\
\mathrm{HHHE} & 10000 & 9500 & 9000 & 5711 & 5961 & 5061 & 4989 \\
\mathrm{HHHH} & 10000 & 9500 & 9000 & 5711 & 5961 & 5061 & 3369 \\
\end{array}
\]

The $\mathrm{H}$ means that the corresponding problem is "hard", the $\mathrm{E}$ means that the corresponding
problem is not "hard". We can observe the obvious skip effect at all.

@@

We would like to see the later problem tend to facing buru solver, so the difficulty effect will decrease.

I use dummy variable like above discussion again, even thougn a countinuous decrease tendency is expected,
but I can't see a method that can transform it to a linear model easily.

The model specification is:

\[
solve_i = \beta_1 solve_{i-1} + \beta_2 solve_{i-2} + \beta_3 solve_{i-3} + \beta_4 hard \, solve_{i-1} +
		  \beta_5 hard_i \, right_i \, solve_{i-1} + \epsilon_i
\]

The dummy variable $left_i$ take 1 if the ith problem is in second half part.

\begin{center}
\begin{tabular}{lclc}
\toprule
\textbf{Dep. Variable:}           &      solve       & \textbf{  R-squared:         } &     0.968   \\
\textbf{Model:}                   &       OLS        & \textbf{  Adj. R-squared:    } &     0.967   \\
\textbf{Method:}                  &  Least Squares   & \textbf{  F-statistic:       } &     1523.   \\
\textbf{Date:}                    & Sat, 13 May 2017 & \textbf{  Prob (F-statistic):} & 4.62e-187   \\
\textbf{Time:}                    &     14:03:17     & \textbf{  Log-Likelihood:    } &   -2745.3   \\
\textbf{No. Observations:}        &         259      & \textbf{  AIC:               } &     5501.   \\
\textbf{Df Residuals:}            &         254      & \textbf{  BIC:               } &     5518.   \\
\textbf{Df Model:}                &           5      & \textbf{                     } &             \\
\bottomrule
\end{tabular}
\begin{tabular}{lccccc}
                                  & \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$>$$|$t$|$} & \textbf{[95.0\% Conf. Int.]}  \\
\midrule
\textbf{solve\_l1}                 &       0.5800  &        0.054     &    10.808  &         0.000        &         0.474     0.686       \\
\textbf{solve\_l2}                 &       0.1706  &        0.063     &     2.728  &         0.007        &         0.047     0.294       \\
\textbf{solve\_l3}                 &       0.1303  &        0.046     &     2.809  &         0.005        &         0.039     0.222       \\
\textbf{diff\_hard:solve\_l1}       &      -0.3482  &        0.163     &    -2.131  &         0.034        &        -0.670    -0.026       \\
\textbf{diff\_hard:solve\_l1:right} &       0.1162  &        0.329     &     0.353  &         0.725        &        -0.532     0.765       \\
\bottomrule
\end{tabular}
\begin{tabular}{lclc}
\textbf{Omnibus:}       & 94.967 & \textbf{  Durbin-Watson:     } &     2.375  \\
\textbf{Prob(Omnibus):} &  0.000 & \textbf{  Jarque-Bera (JB):  } &  1216.730  \\
\textbf{Skew:}          &  1.059 & \textbf{  Prob(JB):          } & 6.17e-265  \\
\textbf{Kurtosis:}      & 13.405 & \textbf{  Cond. No.          } &      62.1  \\
\bottomrule
\end{tabular}
%\caption{OLS Regression Results}
\end{center}

So we can confirm that it is true that solver try to solve latter problem has more steady belief.
The dummy variable method can't be used futher since the condition number has implies the rise of multicolinearity.

@@

I have build a more realistic probility model and fail to extend it as you see. 
Then I develope a indirect time series like model to verify some hypothesis. I can draw conclusion from these survey:

1. Difficulty shock exists significance but it has not memory 
2. The boru solver seems stable more than raw solver when they encounter hard problem.
